Predicting tree failure likelihood for utility risk mitigation via artificial intelligence

### 2021-03-04 docs/manuscript/manuscript.tex
Summarized macro-average metrics

\begin{table}[h!]
    \centering
    \begin{tabular}{l l c}\toprule
    \bf Symbol            & \bf Definition  \\\midrule
    $i$     &  \ Given observation \\
    $c$          & \ Class\\
    $s_c$        & \ Class-specified score \\
    $\hat y_i$       & \ Predicted class of a given observation \\
    $y_i$        & \ Observed (true) class of a given observation \\
    $f(s_c)$        & \ Softmax activation function \\
    $p_{i,c}$        & \ Predicted probability that the i\textsuperscript{th} observation belongs to class $c$ \\
    $L^{CE}_i$        & \ Categorical cross entropy loss function of a single observation \\
    $Pr$ & \ Precision \\
    $Re$ & \ Recall \\
    $F_1$ & \ $F_1$ score \\\bottomrule
    \end{tabular}
    \caption{Symbols description}
    \label{tab:symbols}
\end{table}

>>>>

\begin{table}[h!]
    \centering
    \begin{tabular}{l l c}\toprule
    \bf Symbol            & \bf Definition  \\\midrule
    $i$     &  \ Given observation \\
    $c$          & \ Class\\
    $s_c$        & \ Class-specified score \\
    $\hat y_i$       & \ Predicted class of a given observation \\
    $y_i$        & \ Observed (true) class of a given observation \\
    $f(s_c)$        & \ Softmax activation function \\
    $p_{i,c}$        & \ Predicted probability that the i\textsuperscript{th} observation belongs to class $c$ \\
    $L^{CE}_i$        & \ Categorical cross entropy loss function of a single observation \\
    $Pr_c$ & \ Class-specific precision \\
    $Re_c$ & \ Class-specific recall \\
    $Pr^m$ & \ Macro-average precision \\
    $Re^m$ & \ Macro-average recall \\
    $F_1^m$ & \ Macro-average $F_1$ score \\\bottomrule
    \end{tabular}
    \caption{Symbols description}
    \label{tab:symbols}
\end{table}
